---
title: 'Study 1: Manipulate MOC Stance'
author: "Michelle Shteyn"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Attach packages
library(tidyverse)
library(janitor)
library(here)
library(kableExtra)
library(effsize)
library(broom)
library(aod)
library(haven)
library(here)
library(readr)
library(irr)
library(pwr2)
library(pwr)
```

# Power Analysis: Sample size calculation for balanced 2-way ANOVA

Calculating power for a 2 (activists’ political orientation: liberal vs. center) x 2 (policy stance of hypothetical legislator: not at all likely to support vs. moderately likely to support) between-subjects mixed design to test the effects of target’s policy stance and perceived similarity on activists’ choice of, perceived effectiveness, and perceived fluency of two competing 'Long-Term' frames. 

Power analysis indicates that total sample size should be 404. Will recruit an extra 20% to account for attrition, so 

```{r, include=FALSE}
#a = number of groups in Factor A, Political ID of activist (2: Lib, Center)
#b = number of groups in Factor B, MOC Stance (2: Extremely Opposed vs. Moderately Opposed)
#beta = Type II error probability. if the target power is 85%
#(=0.85), the corresponding beta equals 0.15.
#f.A = effect size of factor A (activist political ID)
#f.B = effect size of factor B (MOC stance)
#B = iteration times, default is 100

#I'm saying effect size of fA should be 0 bc I think all activists (regardless of lib or center) would choose the people/enviro messsage frame
ss.2way(a=2, b=2, alpha=0.05, beta=0.15, f.A = 0.0, f.B=0.5, 
        delta.A=NULL, delta.B=NULL, sigma.A=NULL, sigma.B=NULL, B=100)

#Total sample should be 404. Add extra 20% to account for attrition:
404*1.20 #484.8



#What about if I just do power analysis for an independent samples t-test?

```





To calculate power, specify effect size (w), sample size (N), and degrees of freedom, which is the number of categories minus 1 (df = 4 - 1). 
We also need degrees of freedom. df = (2 - 1) * (2 - 1) = 1

```{r}
pwr.chisq.test(w = .8, power = 0.8, df = 1, sig.level = 0.05)

for a 2x2 ANOVA that tests effect of activist party and MOC stance on perceived effectiveness of messages with a strong effect size to acheive 80% power, we need


#a = number of groups in Factor A, Political ID (2: Dem, Rep, Independent)
#B = number of groups in Factor B, Treatment Condition (2: Tx vs. C)
#beta = Type II error probability. if the target power is 85%
        #(=0.85), the corresponding beta equals 0.15.
#f.A = effect size of factor A (Politcal ID)
#f.B = effect size of factor B  (Treatment Condition)

ss.2way(a=3, b=2, alpha=0.05, beta=0.15, f.A=0.74, f.B=0.075,
        delta.A=NULL, delta.B=NULL, sigma.A=NULL, sigma.B=NULL, B=100)

#Balanced two-way analysis of variance sample size adjustment 

#a = 3
#b = 2
#sig.level = 0.05
#power = 0.85
#n = 101

#NOTE: n is number in each group, total sample = 606


```

pwr.chisq.test(w = .8, power = 0.8, df = 1, sig.level = 0.05)



pwr.chisq.test(w=ES.w1(null,alt), df=(4-1), power=0.8, sig.level = 0.05)


#If I do the average effect sizes of aov 2 and 3, f.A =0.74, f.B =7.5

#___________________________________________________________________

#     POWER ANALYSIS: Sample size calculation for balanced 2-way ANOVA

#___________________________________________________________________
#a = number of groups in Factor A, Political ID (2: Dem, Rep, Independent)
#B = number of groups in Factor B, Treatment Condition (2: Tx vs. C)
#beta = Type II error probability. if the target power is 85%
        #(=0.85), the corresponding beta equals 0.15.
#f.A = effect size of factor A (Politcal ID)
#f.B = effect size of factor B  (Treatment Condition)

ss.2way(a=3, b=2, alpha=0.05, beta=0.15, f.A=0.74, f.B=0.075,
        delta.A=NULL, delta.B=NULL, sigma.A=NULL, sigma.B=NULL, B=100)

#Balanced two-way analysis of variance sample size adjustment 

#a = 3
#b = 2
#sig.level = 0.05
#power = 0.85
#n = 101

#NOTE: n is number in each group, total sample = 606

#If we make these groups representative of the political makeup of the Montecito sample:
#Prop Dem: 280/523 = .53537 * 606 = 324 Dems
#Prop Rep: 144/523 = .27533 * 606 = 167 Reps
#Prop Ind: 99/523 = .18929 * 606 = 115 Independents

#______________________________________________________________________

