---
title: 'Study 1: Manipulate MOC Stance'
author: "Michelle Shteyn"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Attach packages
library(tidyverse)
library(janitor)
library(here)
library(kableExtra)
library(effsize)
library(broom)
library(aod)
library(haven)
library(here)
library(readr)
library(irr)
library(pwr2)
library(pwr)
```

# Power Analysis: Sample size calculation for balanced 2-way ANOVA

Calculating power for a 2 (activists’ political orientation: liberal vs. center) x 2 (policy stance of hypothetical legislator: not at all likely to support vs. moderately likely to support) between-subjects mixed design to test the effects of target’s policy stance and perceived similarity on activists’ choice of, perceived effectiveness, and perceived fluency of two competing 'Long-Term' frames. 

Power analysis indicates that total sample size should be 404. Will recruit an extra 20% to account for attrition, so 485. 

Power analysis for independent samples t-test necessitates 58; extra 20% = 70.

```{r, include=FALSE}
#a = number of groups in Factor A, Political ID of activist (2: Lib, Center)
#b = number of groups in Factor B, MOC Stance (2: Extremely Opposed vs. Moderately Opposed)
#beta = Type II error probability. if the target power is 85%
#(=0.85), the corresponding beta equals 0.15.
#f.A = effect size of factor A (activist political ID)
#f.B = effect size of factor B (MOC stance)
#B = iteration times, default is 100

#I'm saying effect size of fA should be 0 bc I think all activists (regardless of lib or center) would choose the people/enviro messsage frame
ss.2way(a=2, b=2, alpha=0.05, beta=0.15, f.A = 0.0, f.B=0.5, 
        delta.A=NULL, delta.B=NULL, sigma.A=NULL, sigma.B=NULL, B=100)

#Total sample should be 404. Add extra 20% to account for attrition:
404*1.20 #484.8

#What about if I just do power analysis for an independent samples t-test?
pwr.t.test(d=0.5,power=0.85,sig.level=0.05,type="two.sample",alternative="greater") #We would need n = 58. Add extra 20%:
58*1.20 #70

```





